---
title: "TakeHomeExam2"
author: "Kyle Kurkela"
date: "3/24/2021"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lavaan)
library(tidyverse)

fomo.df <- read_csv('fomo.csv', col_types = cols())
```

## Model 1

### 1. Model in Equation Form. 

$$\begin{bmatrix} Y1 \\ Y2 \end{bmatrix} = 
\begin{bmatrix} 0 & 0 \\ \beta_{21} & 0  \end{bmatrix} 
\begin{bmatrix} Y1 \\ Y2 \end{bmatrix} +
\begin{bmatrix} \gamma_{11} & 0 \\ \gamma_{12} & 0 \end{bmatrix}
\begin{bmatrix} X1 \\ X2 \end{bmatrix} + 
\begin{bmatrix} \zeta_{1} \\ \zeta_{2} \end{bmatrix}$$

$\boldsymbol{\beta} = \begin{bmatrix} 0 & 0 \\ \beta_{21} & 0  \end{bmatrix}$  
$\boldsymbol{\Gamma} = \begin{bmatrix} \gamma_{11} & 0 \\ \gamma_{12} & 0 \end{bmatrix}$  
$\boldsymbol{\Phi} = \begin{bmatrix} \phi_{11} & \\ \phi_{21} & \phi_{22}\end{bmatrix}$  
$\boldsymbol{\Psi} = \begin{bmatrix} \psi_{11} & \\ 0 & \psi_{22} \end{bmatrix}$  

### 2. Count the number of parameters. Compute the degrees of freedom.

+ Free Parameters: 8  
+ df: 2

### 3. Copy and paste R syntax. 

```{r}
m1 <- '
FOMO ~ Boredom
Boredom ~ Anxiety + Dep
Anxiety~~Anxiety
Dep~~Dep
Anxiety~~Dep
Boredom~~Boredom
FOMO~~FOMO
'

model1.fit <- lavaan(model = m1, data = fomo.df)
```

### 4. Copy and paste the "inspect" output. 

```{r}
inspect(model1.fit, )
```

